DATA 621 Homework #4

### 2019-11-08 hw4/HW4.Rmd
Imputing values function added and added some density variables

```{r, null_prefix = TRUE}
# set.seed(42)
# knn <- df %>%
#   select(-TARGET_FLAG, -TARGET_AMT, is.numeric()) %>%
#   #na.omit() %>%
#   knnImputation()
# 
# for(var in names(df)){
#   impute_me <- is.na(df[[var]])
#   if (nrow(df[impute_me,]) > 0){
#     print(paste("Fixing the", nrow(df[impute_me,]), "missing values in", var, "(df)"))
#     #df[impute_me, var] <- knn[impute_me, var] 
#   }
# }
```

@@

df <- feature_creation(df)
evaluation <- feature_creation(evaluation)
```

@@

>>>>

```{r, null_prefix = TRUE}
# set.seed(42)
# knn <- df %>%
#   select(-TARGET_FLAG, -TARGET_AMT, is.numeric()) %>%
#   #na.omit() %>%
#   knnImputation()
# 
for(var in names(df)){
  impute_me <- is.na(df[[var]])
  if (nrow(df[impute_me,]) > 0){
    print(paste("Fixing the", nrow(df[impute_me,]), "missing values in", var, "(df)"))
    #df[impute_me, var] <- knn[impute_me, var] 
  }
}

## adding in some imputing logic
library(VIM)
library(laeken)

df[,3:ncol(df)] <- df[,3:ncol(df)] %>% kNN(numFun = weightedMean, weightDist=TRUE)
```

@@

df <- feature_creation(df)
evaluation <- feature_creation(evaluation)

df$TARGET_FLAG_BOOL <- ifelse(df$TARGET_FLAG=="1",1,0)
```

@@

```{r}
library(lme4)
glm <- glm(TARGET_AMT ~ .-TARGET_FLAG-TARGET_FLAG_BOOL , data= train, family=poisson) 
summary(glm)

test$Prediction =predict.glm(glm, newdata=test, type="response")

cor(test$TARGET_AMT, test$Prediction)

glm2 <- glm(TARGET_AMT ~ .-TARGET_FLAG-TARGET_FLAG_BOOL , data= train) 
summary(glm2)

test$Prediction2 =predict.glm(glm2, newdata=test, type="response")

cor(test$TARGET_AMT, test$Prediction)

glm3 <- glm(TARGET_AMT ~ AGE+PARENT1+MSTATUS+JOB+BLUEBOOK+TIF+CAR_AGE_density+URBANICITY+MVR_PTS+REVOKED+CLM_FREQ+OLDCLAIM , data= train, family=poisson) 
summary(glm3)

test$Prediction =predict.glm(glm3, newdata=test, type="response")

cor(test$TARGET_AMT, test$Prediction)
```

```{r}
source("https://raw.githubusercontent.com/crarnouts/Corey-s_Scripts_For_Reference/master/11_5_19_Density_Diff_Function")
```

### Creating Some New Variables

```{r}

## try it out 
train <- density_diff(train,test,"INCOME",train$TARGET_FLAG_BOOL,"income_density")$new_data_training
test <- density_diff(train,test,"INCOME",train$TARGET_FLAG_BOOL,"income_density")$new_data_eval

density_diff(train,test,"INCOME",train$TARGET_FLAG_BOOL,"income_density")$dist_diff
density_diff(train,test,"INCOME",train$TARGET_FLAG_BOOL,"income_density")$dist

train <- density_diff(train,test,"CAR_AGE",train$TARGET_FLAG_BOOL,"CAR_AGE_density")$new_data_training
test <- density_diff(train,test,"CAR_AGE",train$TARGET_FLAG_BOOL,"CAR_AGE_density")$new_data_eval

density_diff(train,test,"CAR_AGE",train$TARGET_FLAG_BOOL,"CAR_AGE_density")$dist_diff
density_diff(train,test,"CAR_AGE",train$TARGET_FLAG_BOOL,"CAR_AGE_density")$dist

train <- density_diff(train,test,"TRAVTIME",train$TARGET_FLAG_BOOL,"TRAVTIME_density")$new_data_training
test <- density_diff(train,test,"TRAVTIME",train$TARGET_FLAG_BOOL,"TRAVTIME_density")$new_data_eval

density_diff(train,test,"TRAVTIME",train$TARGET_FLAG_BOOL,"TRAVTIME_density")$dist_diff
density_diff(train,test,"TRAVTIME",train$TARGET_FLAG_BOOL,"TRAVTIME_density")$dist

```

##Test out Some Models

```{r}

```
